\chapter{Available ATC positions}\
\section{Delivery [DEL]}

Clearance delivery position is responsible for delivery of start-up and ATC clearances to departing flights.

Delivery's responsibilities include:
\begin{itemize}
    \item checking the correctness of the flight plan and clarifying any mistakes contained therein,
    \item assignment of standard departure instructions (runway, SID),
    \item coordination of non-standard departure instructions with other controllers, such as:
    \begin{itemize}
        \item departure from a runway other than the active one,
        \item inability to perform SID,
        \item VFR flight in CTR,
    \end{itemize}
    \item transmission of weather information (current ATIS or, if it is not available, reading of the latest METAR),
    \item if the traffic flow manager orders the introduction of slots, informing the pilots about delays and allocated slots.
\end{itemize}

Rules for transferring aircraft from Delivery to the next controller:
\begin{itemize}
    \item Delivery asks the crew after issuing permission to report readiness to push/launch,
    \item when the crew reports readiness, the Delivery controller, based on coordination and traffic situation:
    \begin{itemize}
        \item at a remote (''pass-through'') stand, after coordination with the GND controller, approves engine start-up,
        \item at gate (requiring pushback), transfers communication to the next controller (GND).
    \end{itemize}
\end{itemize}

If the aircraft has to wait (e.g.\ due to slot or traffic situation), DEL informs the crew to remain on its frequency and transfers communications only when the aircraft will be able to start the pushback and/or start-up.

\section{Operation coordinator ``Planner'' [P\_DEL]}

Planner position is not a standard position. A planner is appointed in the following cases:
\begin{itemize}
    \item an event with a large amount of traffic is planned,
    \item traffic exceeds operational capacity of currently logged in controllers.
\end{itemize}

Planner's responsibilities include:
\begin{itemize}
    \item slot assignment,
    \item coordination with Delivery.
\end{itemize}

Slots are assigned based on:
\begin{itemize}
    \item previously set schedule (e.g.\ during events),
    \item pilot login times and planned EOBT.\@
\end{itemize}

\section{Ground [GND]}

Ground controller's responsibilities include:
\begin{itemize}
    \item issuing start-up and push back clearances,
    \item managing ground traffic in manoeuvring area of the aerodrome,
    \item queuing departures and avoiding delays during heavy traffic,
    \item informing flight crews of all significant changes in weather information, \textbf{including QNH changes},
    \item covering Delivery's responsibilities when DEL is offline or no DEL has been set at the aerodrome.
\end{itemize}

Transfer rules of departing aircraft from Ground to the next controller:
\begin{itemize}
    \item by default, aircraft are being transferred by \textit{``contact''} when approaching the holding point,
    \item by next controller's request, aircraft may be transferred usint \textit{``monitor''},
    \item transfer shall take place only if there is reasonable certainty that no conflict with other ground traffic will emerge and the crew will not require any further instructions from the GND controller,
    \item in a long departure queue, aircraft should be transferred to the next controller when it is probable that the next controller will need to issue an instruction to the aircraft.
\end{itemize}

\section{Tower [TWR]}

Tower's responsibilities include:
\begin{itemize}
    \item Air Traffic Control within the CTR, including controlling VFR flights,
    \item control of IFR flights during approaches and of all operations on the runways,
    \item providing ATIS information (on selected aerodromes) or, on request, weather information, including informing crews of QNH changes,
    \item covering Ground's responsibilities when GND is offline or no GND has been set at the aerodrome.
\end{itemize}

Aerodrome traffic control is conducted according to the procedures for aerodrome control service, described in detail in chapters 6 and 7 of ICAO Doc 4444. The most important information and procedures have been described in the following Operations Manual both in general (to be used in all controlled aerodromes) and in detail (including local procedure deviations for aerodromes).